Enhanced Material Point Method to face dynamic problems: Local-maximum entropy approximation and explicit predictor-corrector scheme\\ \red{On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}

### 2020-04-27 LME-MPM.tex
Cambios Figuras e Introducción

\usepackage{lineno,hyperref}
\usepackage{float}
\usepackage{subfig}
\usepackage{color}
\usepackage{soul}
\usepackage{cancel}

@@

\newcommand{\vect}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\tens}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Matrix}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Vector}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\red}[1]{
  \textcolor{red}{{#1}}
}
% Divergence
\newcommand{\Div}[1]{
  \ensuremath{div({#1})}
}
% Gradient
\newcommand\Grad[1]{grad({#1})}
\newcommand\GradS[1]{grad^s({#1})}
\newcommand\GradT[1]{grad^T({#1})}
% Partial derivative
\newcommand{\Deriv}[3][]{
  \ensuremath{\frac{\partial^{#1}{#2}}{ \partial {#3}^{#1} }}
}
% Integral
\newcommand{\Integral}[2]{
  \IfStrEqCase{#1}{
    {2}{\ensuremath{\int_{\varGamma_d}{#2}\ d\varGamma}}
    {3}{\ensuremath{\int_{\varOmega}{#2}\ d\varOmega}}
  }
}

@@

@@

The aforementioned techniques are devoted to mitigate the
``grid crossing'' error. Nevertheless, in the presence of shock waves spurious,
numerical noises appear despite of the employment of these
techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
as wiggles, arise due to inaccuracies in the time discretization technique.
A simple approach to face those spurious noises lies on the addition of nonphysical damping sources to the equilibrium equations. This
approach has been widely employed in this and many other numerical
techniques. To avoid introducing this nonphysical sources, many
researchers has proposed alternative time integration
schemes which reduce the presence of high frequency noises by
filtering them or increasing \red{somehow} the accuracy. \cancel{of the time integration
scheme.} One of the most popular is the \acrfull{igimp}
Charlton {\it et al.} (2017)~\cite{Charlton2017} \red{DECIR MAS DE ESTO}. More recently Tran \&
Solowski (2019)~\cite{Tran2019e} proposed a generalised-$\alpha$ scheme
for \acrshort{mpm} with promising results but at the expense of increasing
the computational effort. In this paper a less time consuming and high
efficient explicit predictor-corrector integration method has been
proposed. It consists in an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
has been chosen among other suitable alternatives as those proposed
by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
(1993)~\cite{Geranlized_alpha_1993} because its simplicity and its good
performance dealing with solid dynamic problems under a meshfree
framework in~\cite{Navas2018a}.

>>>>

\usepackage{lineno}
% \usepackage{hredyperref}
\usepackage{float}
\usepackage{subfig}
\usepackage{color}
\usepackage{soul}
\usepackage{cancel}

@@

\newcommand{\vect}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\tens}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Matrix}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Vector}[1]{
  \ensuremath{\mathbf{{#1}}}
}
% Divergence
\newcommand{\Div}[1]{
  \ensuremath{div({#1})}
}
% Gradient
\newcommand\Grad[1]{grad({#1})}
\newcommand\GradS[1]{grad^s({#1})}
\newcommand\GradT[1]{grad^T({#1})}
% Partial derivative
\newcommand{\Deriv}[3][]{
  \ensuremath{\frac{\partial^{#1}{#2}}{ \partial {#3}^{#1} }}
}
% Integral
\newcommand{\Integral}[2]{
  \IfStrEqCase{#1}{
    {2}{\ensuremath{\int_{\varGamma_d}{#2}\ d\varGamma}}
    {3}{\ensuremath{\int_{\varOmega}{#2}\ d\varOmega}}
  }
}

@@

\newcommand{\red}[1]{
  \textcolor{red}{{#1}}
}

\newcommand{\MMP}[1]{
  \textcolor{blue}{{#1}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The aforementioned techniques are devoted to mitigate the
``grid crossing'' error. Nevertheless, in the presence of shock waves spurious,
numerical noises appear despite of the employment of these
techniques~\cite{Tran2019e}. These numerical inaccuracies, also known
as wiggles, arise due to inaccuracies in the time discretization technique.
A simple approach to face those spurious noises lies on the addition of nonphysical damping sources to the equilibrium equations. This
approach has been widely employed in this and many other numerical
techniques. To avoid introducing this nonphysical sources, many
researchers has proposed alternative time integration
schemes which reduce the presence of high frequency noises by
filtering them or increasing \red{somehow} the accuracy. \cancel{of
  the time integration scheme.} \MMP{One of the first attempts of it was
the proposal of an implicit time integration scheme by Guilkey \&
Weiss \cite{Guilkey_2003}. More recently Wang {\it et al.}
\cite{Wang_2016} to downsize this spurious noises add a nonvoiscous
damping to the linear momentum balance equation, and later Charlton
{\it et al.} \cite{Charlton_2017} extended this scheme to the
\acrshort{gimp} approach, and introducing the well-know
\acrfull{igimp} method. However, the local damping introduced by
\cite{Wang_2016} can totally over-damp the solution in time-dependent
simulations such as in consolidation process. Within the explicit
time integration schemes, Lu {\it et al.}\cite{LU_2018} introduced the time-discontinuous Galerkin method to control the spurious noises
propagation, and later Tran \& Solowski~\cite{Tran2019e}
proposed a generalised-$\alpha$ scheme for \acrshort{mpm} with
promising results but at the expense of increasing the computational
effort.}
In this paper a less time consuming and high efficient explicit predictor-corrector integration method has been
proposed. It consists in an accommodation of the traditional \acrsull{npc} scheme, widely employed in Finite Element methods. This method
has been chosen among other suitable alternatives as those proposed
by Wilson {\it et al.} (1972)~\cite{Wilson1972} or Chung \& Hulbert
(1993)~\cite{Geranlized_alpha_1993} because its simplicity and its good
performance dealing with solid dynamic problems under a meshfree
framework in~\cite{Navas2018a}.
